\Title

### 2021-06-09 manuscript/content.tex
Replace outperform for underperform

With the goal of highlighting the importance of randomizing the order in which
the overlapping windows are iterated, we interpolated the airborne synthetic
survey using the same estimated values for the \emph{damping} and
\emph{depth} but disabling the random shuffling of the windows, iterating over
them in sequential order.
Fig.~\ref{fig:eql-boost-airborne}c shows the differences between the target
grid and the predictions made by the gradient-boosted equivalent sources
without random shuffling the windows.
Fig.~\ref{fig:eql-boost-airborne}d shows the RMS error of the
residuals after each iteration.
These results show how the gradient-boosted equivalent sources outperform by
iterating over the overlapping windows in sequential order: they fail to
produce realistic and accurate predictions while the speed in which the
algorithm converges is considerable smaller.

>>>>

With the goal of highlighting the importance of randomizing the order in which
the overlapping windows are iterated, we interpolated the airborne synthetic
survey using the same estimated values for the \emph{damping} and
\emph{depth} but disabling the random shuffling of the windows, iterating over
them in sequential order.
Fig.~\ref{fig:eql-boost-airborne}c shows the differences between the target
grid and the predictions made by the gradient-boosted equivalent sources
without random shuffling the windows.
Fig.~\ref{fig:eql-boost-airborne}d shows the RMS error of the
residuals after each iteration.
These results show how the gradient-boosted equivalent sources underperform by
iterating over the overlapping windows in sequential order: they fail to
produce realistic and accurate predictions while the speed in which the
algorithm converges is considerable smaller.
